---
title: "Egonetzwerk Irina"
output: html_notebook
---

```{r Egonetzwerk einlesen mit Listen}
library("igraph")  
library("igraphdata")
# Read Edgelist
edges <- read.csv("Egonetzwerk - Edges-2.csv", header=T, as.is=T, sep = ",") # liest die Edgelist ein
nodes <- read.csv("EgonetzwerkNodes.csv", header=T, as.is=T, sep=",") #liest die Nodelist ein
matrix <- as.matrix(edges) # erstellt eine Matrix aus den Edges 
irina <- graph_from_data_frame(d=edges, directed=FALSE) # erstellt den Graph mit dem Namen irina
```

```{r}
plot(irina,vertex.label=c("Ellen","Katharina H","Katharina Y","Greta","Irina"),
     vertext.label.color="black",
     main="Egonetzwerk", 
     sub="Beziehungen",
     vertex.size=10,
     vertex.color="lightblue",
     weighted=TRUE,
     vertex.frame.color=NA)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

